Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-08-25 manu-draft.Rmd
Suggested title edits for your consideration.

---
title: "Initial environmental impacts of Piney Point wastewater discharge into Tampa Bay, Florida"
output: 
  bookdown::word_document2:
    reference_docx: my_styles.docx
    number_sections: false
always_allow_html: true
bibliography: refs.bib
author: "Marcus W. Beck (mbeck@tbep.org), Gary E. Raulerson (graulerson@tbep.org), Maya C. Burke (mburke@tbep.org), Joe Whalen (jwhalen@tbep.org), Sheila Scolaro (sscolar@tbep.org), Ed T. Sherwood (esherwood@tbep.org)"
urlcolor: blue
csl: marine-pollution-bulletin.csl
link-citations: true
---

>>>>

---
title: "Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida"
output: 
  bookdown::word_document2:
    reference_docx: my_styles.docx
    number_sections: false
always_allow_html: true
bibliography: refs.bib
author: "Marcus W. Beck (mbeck@tbep.org), Gary E. Raulerson (graulerson@tbep.org), Maya C. Burke (mburke@tbep.org), Joe Whalen (jwhalen@tbep.org), Sheila Scolaro (sscolar@tbep.org), Ed T. Sherwood (esherwood@tbep.org)"
urlcolor: blue
csl: marine-pollution-bulletin.csl
link-citations: true
---
